### 2025-05-05 Chapters/paper1.tex
changes

@@

@@

\section{Results and Evaluation}

This section presents the results and evaluations for the models trained, including Random Forest, Bagging, Ensemble Learning, and Gradient Boosting. The following figures summarize the performance metrics for each model.

@@

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\linewidth]{"img/paper_1/k-FOLD.PNG"}
	\caption{Architecture of Machine Learning Classifiers for Sleep Stage
		Classificatio}
	\label{fig:architechture1}
\end{figure}

@@

\subsection{Random Forest with K-Fold Cross-Validation Pipeline}

The model pipeline was created using \texttt{make\_pipeline} from \texttt{sklearn.pipeline}, which integrates two main components: a function transformer and a random forest classifier. The function transformer is applied to extract the EEG power bands from the data, which are then used as features for training the model. The \texttt{RandomForestClassifier} was chosen for its ability to perform well with high-dimensional data, and it was set with 100 estimators to ensure robust performance. The random forest classifier was trained and tested on each fold using the 5-fold cross-validation setup, providing an unbiased evaluation of the model’s performance.

\subsection{Ensemble Classifier with K-Fold Cross-Validation Pipeline}

The pipeline was constructed using \texttt{make\_pipeline} from \texttt{sklearn.pipeline}, which integrates a function transformer for extracting EEG power bands as features and an ensemble classifier for prediction. The function transformer applies the \texttt{eeg\_power\_band} function to preprocess the data, and the \texttt{VotingClassifier} combines the predictions from a \texttt{RandomForestClassifier} and  The ensemble classifier was trained and tested on each fold using the 5-fold cross-validation setup, offering a more robust evaluation by leveraging the strengths of both classifiers.

\subsection{Gradient Boosting with K-Fold Cross-Validation Pipeline}
In this section, we employed Gradient Boosting with 5-fold cross-validation to classify the EEG data. Gradient Boosting is an ensemble learning technique that builds models sequentially, where each model attempts to correct the errors made by the previous ones. This method can improve predictive performance by focusing on difficult-to-predict instances. The dataset was split into five subsets, and each subset was used as the test set once, while the remaining four were used for training. The model's generalization ability was thus thoroughly evaluated.

A pipeline was constructed using \texttt{make\_pipeline} from \texttt{sklearn.pipeline}. It incorporates a function transformer that preprocesses the EEG data by extracting power band features through the \texttt{eeg\_power\_band} function. The processed data is then passed to a \texttt{GradientBoostingClassifier}, which is used for prediction. The \texttt{KFold} cross-validation technique with 5 splits ensures that the model is trained and validated on different portions of the dataset, offering a reliable estimate of its performance.

@@

\section{Results and Evaluation With Machine Learning }

@@

\section{Results and Evaluation with K-fold Cross Validation }

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/Ensemble Learning_percentage_based.png}
		\caption{Ensemble Learning Confusion Matrix }
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/Random Forest_percentage_based.png}
		\caption{Random Forest Confusion Matrix }
	\end{minipage}

	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/GB Classifier_percentage_based.png}
		\caption{GB Classifier Confusion Matrix }
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/SGD_percentage_based.png}
		\caption{SGD Confusion Matrix }
	\end{minipage}
\end{figure}

\section{Comparison Sections}

\begin{figure}[H]
	\centering
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/accuracy_comparison.png}
		\caption{Accuracy Comparison}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/bar_chart_improved.png}
		\caption{Improved Bar Chart}
	\end{minipage}

	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/box_plot_comparison.png}
		\caption{Box Plot Comparison}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth]{img/paper_1/violin_plot_improved.png}
		\caption{Improved Violin Plot}
	\end{minipage}
\end{figure}
